\section{Introduction} \label{sec:introduction}

The Autonomous Learning Robot provides an excellent opportunity to demonstrate the techniques and methods of Artificial Intelligence. It efficiently utilizes the application of various AI themes like Vision, Learning and autonomous Agent based task accomplishment. Artificial Intelligence is an upcoming field that has attracted research attention and under active development. Owing to this development the resources required to learn and implement its concepts, on an individual user’s scale, have now become accessible. In the process of learning we aim to build upon existing systems, taking a step towards Artificial General Intelligence.

The project will employ concepts from Dynamic Programming for path calculation, Artificial Neural Networks for Machine Learning as a part of Artificial Intelligence, Computer Vision using Digital Image Processing, Natural Language Processing for Speech Recognition, Spatial Mapping to analyze environmental risk of execution of user commands.

Open AI is a non-profit artificial intelligence (AI) research company, associated with business magnate Elon Musk, that aims to carefully promote and develop open-source friendly AI in such a way as to benefit, rather than harm, humanity as a whole. The organization aims to "freely collaborate" with other institutions and researchers by making its patents and research open to the public.

Repurposing industrial robots for daily tasks using machine learning is one branch of OpenAI’s current work. At national level also, research is conducted by Artificial Intelligence Association of India (AIAI) on theory, design, application, and development of the mechanisms underlying thought and intelligent behavior and their embodiment in machines emphasizing intelligent agent systems, knowledge engineering, language technologies, cognitive systems, robotics and human-computer interaction in which these paradigms are contained.

Currently, most hardware oriented applications consist of a procedural approach towards implementation of autonomy. However, Artificial Narrow Intelligence is being integrated at a rapid rate. We aim to initiate a transition towards Artificial General Intelligence by expanding upon the avenues to which ANI is being applied and coalescing these into a step in the direction of AGI. 



